The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-04 article.tex
First sketch of abstract

  % One or two sentences providing a basic
  % introduction to the field,
  % comprehensible to a scientist in any discipline.
  Phylogenetics is the field in which phylogenies are
  created from DNA, RNA or protein alignments.
  The evolutionary relationships between species or
  individuals

  % Two to three sentences of
  % more detailed background, comprehensible to
  % scientists in related disciplines.

  % One sentence clearly stating the general
  % problem being addressed by this particular
  % study.

  % One sentence summarising the main
  % result (with the words “here we show”
  % their equivalent).

@@

\item The (constant-rate) birth-death (BD) model 
embodies the common assumption that 
only a single speciation event can occur at any given time.
The multiple-birth-death (MBD) model relaxes this assumption, 
allowing events in which 
large-scale environmental changes lead to a great number of species 
in relatively short time intervals. 
Such hypothesis can be useful to describe, for example, 
systems like cichlid fish diversification in the 
African Great Lakes: Malawi, Tanganyika and Victoria 
(\cite{janzen2016}, \cite{janzen2017}).

>>>>

  % One or two sentences providing a basic
  % introduction to the field,
  % comprehensible to a scientist in any discipline.
  There exist millions of species on Earth,
  all originating from a common ancestor billions
  of years ago.
  The field of phylogenetics uses heritable material
  to determine which species are closest related and what are
  the mathematics that shape speciation.

  % Two to three sentences of
  % more detailed background, comprehensible to
  % scientists in related disciplines.
  In Bayesian phylogenetics, a DNA/RNA/protein alignment
  is used to infer a distribution of phylogenies and parameter estimates.
  To do so, we use assumptions that may be biologically unrealistic,
  but may give tolerable errors.

  % One sentence clearly stating the general
  % problem being addressed by this particular
  % study.
  Contemporary inference assumes that speciation
  never co-occurs.

  % One sentence summarising the main
  % result (with the words “here we show”
  % their equivalent).
  Here we show the error we make in our inference,
  when nature has varying degrees of co-occuring speciation.

@@

\richel{duplicate paragraph!}
\item The (constant-rate) birth-death (BD) model 
embodies the common assumption that 
only a single speciation event can occur at any given time.
The multiple-birth-death (MBD) model relaxes this assumption, 
allowing events in which 
large-scale environmental changes lead to a great number of species 
in relatively short time intervals. 
Such hypothesis can be useful to describe, for example, 
systems like cichlid fish diversification in the 
African Great Lakes: Malawi, Tanganyika and Victoria 
(\cite{janzen2016}, \cite{janzen2017}).
